Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\ \begin{large} Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity \end{large}

### 2017-02-06 draft.tex
.

As an additional possibility of spike-train analysis, we looked at potential correlations across neurons within both populations. To do so, we calculated cross-correlations for all possible neuron-pairings within a population, excluding auto-correlations. Figure \ref{Pop_Mean_Cross_Corr} shows the mean cross-correlation taken over all these pairs. Surprisingly, we found a significant increase in correlation across neurons for diffusive homeostasis. 
\begin{figure}
\includegraphics[width=\textwidth]{../../plots/Spike_Stats/pop_mean_cross_corr.png}
\caption{Mean of cross correlation over all pairs of neurons in the respective neuron-group. Significantly higher correlation can be found in both groups for diffusive homeostasis. Spike data was taken from $\mathrm{1400-1500\,s}$ of the simulation.}
\label{Pop_Mean_Cross_Corr}
\end{figure}
When speculating about the root of this discrepancy one could consider two possibilities: Either, it is an immediate consequence of diffusive homeostasis, or it is indirectly related through other mechanisms present within the network. Regarding the first, it is certainly true that some amount of information about the activity of one neuron is transferred to another one in its neighborhood via diffusion. However, due to the time scale of the homeostatic adaption, the response to fluctuations in the diffusive signal is on the order of seconds, while correlations in Figure \ref{Pop_Mean_Cross_Corr} are taking place within milliseconds. Thus, we concluded that a \emph{direct} link between homeostatic signaling and increased correlations can be regarded as implausible and that it must be an effect based on topological differences within the network. We investigate these in Section \ref{Network_Topology_Section}.

@@

Despite of fluctuations within the firing rate on small time scales due to the inherent nature of - approximately - random spike generation, we wanted to know how strongly firing rates of single excitatory cells fluctuate over longer timescales of multiple seconds. This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of "momentary" rates.

A constant "rate" of an approximately randomly spiking neuron means that the dependence of fluctuations of rates onto the width of the averaging window should be identical to a homogeneous poisson process of the same total mean firing rate. As bin sizes increase, possible long-term fluctuations of firing rates can then be identified as deviations from the variance one would expect from a homogeneous process. We tested this in Figure \ref{f_Var_vs_n_Bin}. (A) was taken from $\mathrm{1000-1500\,s}$, which is well inside the phase of diffusive homeostasis. As one can see, the statistics of the three representative neurons are well fitted by the predictions for homogeneous poisson processes with the same mean rate, being a straight line given by $\mathrm{var = f_{mean}\cdot n_{bins}/T_{total}}$, though slight deviations can be seen as a different factor of proportionality. (B) acts as an illustration showing a counterexample: Here, we included the entire time span of the simulation, including the transition between non-diffusive and diffusive homeostasis. For almost all of the neurons, this will cause a transition of firing rate between 3 Hz and a new rate different from 3 Hz. This inhomogeneity is represented by the increasing positive relative deviation from the dashed line for small number of bins (i.e., large bin widths), even increasing again for a very few number of bins.
\begin{figure}
%%% plot_spt_var_vs_bin_width.py
\includegraphics[width=\textwidth]{../../plots/Spike_Stats/sim_f_var_vs_hom_poisson.png}
\caption{A: Relation between Variance of the frequency signal (acquired by binning spikes) and the number of bins within the given time range of $\mathrm{1000-1500\,s}$, taken from three randomly picked excitatory neurons. B: Same procedure as in (A) for a randomly chosen excitatory neuron, but time range was $\mathrm{0-1500\,s}$, which includes the initial phase of non-diffusive homeostasis. In both plots, dashed lines are the expected curve of a homogeneous poisson process of the same mean rate.}
\label{f_Var_vs_n_Bin}
\end{figure}
We therefore concluded that diffusive homeostasis manages to retain firing rates on a constant level, not only population-wise but on a single-cell level as well. In particular, plastic modifications across the network due to STDP and synaptic growth/pruning - which were always acting for all the simulation results presented so far - appeared to be compensated for.

@@

In contrast to our model, Effenberger et al. identified the presence of inhibitory STDP as a necessary mechanism for the development of this feature. On a deeper explanatory level, the authors argue that inhibitory STDP is indirectly involved: It weakens inhibitory currents for some neurons, which cause these neurons to have more above-average firing rates. In turn, synapses between highly active presynaptic cells and postsynaptic neurons with lower activity are known to be subject to long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}. With these causal relations in mind, we can argue that diffusive homeostasis effectively embodies the same functional role as inhibitory STDP in \cite{Effenberger_2015} by allowing for the presence of excitatory cells with above-average activity. We tested this relationship by plotting the mean outgoing weights against the average firing rate, see Figure \ref{Out_Weight_vs_F}. A strong heterogeneity of firing rates allows for the development of few strong synapses, while the distribution of mean weights resulting from a narrow distribution is limited to a smaller range. We also tested the case of instant diffusion. Though firing rates span across a similar range, mean weights do not reach as high values as in the case of diffusion at a finite rate.
\begin{figure}
%%% out_weight_vs_f.py
\includegraphics[width=\textwidth]{../../plots/syn_topology/mean_out_weights_vs_rate.png}
\caption{Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{t=700-1000\,s}$) in regular (A) and logarithmic space (B). Each plot corresponds to a presynaptic excitatory cell.}
\label{Out_Weight_vs_F}
\end{figure}
Furthermore, it is interesting to note that on a logarithmic weight scale, we found a roughly linear relationship. Figure \ref{Out_Weight_vs_F} only depicts data from simulations including a distance dependent connection profile, since removing this topology did not result in noticeable differences.

\section{Further Analysis of the Firing Rate Distribution}
On a preliminary level, the results of section \ref{Fir_Dist_Section} were positive with respect to our goal of achieving a broad and skewed firing rate distribution. Following this, we tried to further gain insight into the actual shape of the resulting distribution. 
\subsection{Review of a Dynamic Mean-Field Model}\label{Mean_Field_Review_Section}
Sweeney et al. attempted to predict the shape of the firing rate distribution by means of a simplified mean-field approximation of diffusion \cite{Sweeney_Paper}. The main simplification within homeostatic feedback was the replacement of Equation \ref{Theta_dyn} by
\begin{equation}
\dot{V_t^i}(t) = \frac{1}{\tau_{HIP}} \left( (1-\alpha)\frac{\phi_i-\phi_0}{\phi_i} +\alpha \frac{\langle \phi \rangle-\phi_0}{\langle \phi \rangle} \right)\;. 
\label{diff_hom_simpl_sweeney}
\end{equation}
$\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acted as a parameter that determines the "mixture" between single-neuron-homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$). $\mathrm{\phi_i}$ and $\mathrm{\mathrm{\langle \phi \rangle}}$ represent individual firing rates and their overall mean.

@@

\includegraphics[width=0.7\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_sim_vs_mat.png}

@@

\subsection{Spreading of NO-sources extends Encoding of Input Heterogeneity}
Since our analytic results revealed that a strong correlation between spatial structure and result firing rates is present if diffusive interaction allows a clear distinction between individual neurons and their spatial neighbors, we considered the possibility that a wider spread of each individual NO-source could locally decrease distinguishability between neurons. Thereby, it might allow input heterogeneities to be encoded over a longer period of time without the need to tweak diffusion to unrealistically high values. The biological plausibility of this idea is discussed in Section \ref{Possible_Modifications_Section}.

@@

Sweeney et al. claimed that their implementation of diffusive homeostasis enables individual neurons to vary their firing rates more flexible compared to single-neuron homeostatic models, especially allowing for sustained encoding of different levels of external input. Interestingly, we could not confirm this, at least within the tests that we performed and the given set of standard parameters. Overall, the resulting behavior of the excitatory population rather appeared to us as a form of single-neuron homeostasis whose individual targets are predetermined by the quenched random spatial structure of the respective cells. In particular, our result depicted in Figure \ref{Ext_Input_Switch} did not support the notion of separability of inputs. Of course, this impression only applies to the case where the aforementioned mixture of influence between spatial and synaptic topology is dominated by the former. By analyzing network activity based on our analytic model, we found that for finite diffusion constants, indeed only a single homeostatic fixed point exists. On a practical level though, the gradual decorrelation with this theoretical state of activity upon larger values of $\mathrm{D}$ is presumably caused by synaptic turnovers, which change the synaptic input. The resulting changes in activity are more slowly and less accurately compensated in the case of larger diffusion constants.

However, for the standard choice of parameters (being roughly based on experimental data), the resulting activity is indeed strongly bound to the spatial structure of excitatory cells. Naturally, this raises the question of biological plausibility. To our knowledge, no experimental study exists that relates measurements of spontaneous activity to local fluctuations of neuronal densities. Ivenshitz and Segal studied the influence of (mean) neuronal density onto neuronal activity in a culture of hippocampal neurons \cite{Ivenshitz_2010}. Lower densities resulted in a more irregular activity, with stronger but less frequent bursting events. However, since our network was tuned to exhibit non-bursting activity, it is hard to draw any conclusions from this result.

@@

A major issue of Equation \eqref{Theta_dyn} is the fact that, given a clamped positive or negative difference between the actual NO concentration and the target concentration, the excitability of the neuron would decrease or increase without bounds. Because of the limited amount of ion channels that exist in a cell and can be affected by nitric oxide, upper and lower bounds should certainly be present. A simple approach to tackle this would be to implement hard bounds into our neuron model, not allowing the threshold to pass an upper and lower value. Another possibility is the implementation of these bounds by means of the differential equation itself.

In either case, such a modification could break the ability of the network to tune thresholds in such a way that necessarily \emph{all} neurons eventually reach target concentration. As a consequence, the fixed point of firing rates under diffusive homeostasis would not be strictly determined by spatial structure, but by a combination of network structure and the neurons' positions. As an example, consider a modification of Equation \eqref{Theta_dyn} of the form
\begin{equation}
\dot{V_t^i}(t) = \frac{1}{\tau_{V_t}}\left(\frac{NO(\mathbf{r}_{neur}^i,t)-NO_0}{NO_0} + \frac{\alpha}{V_t^i - V_{t,min}} + \frac{\alpha}{V_t^i - V_{t,max}}\right) \; .
\label{Theta_dyn_with_Bounds}
\end{equation}
In this form, $\mathrm{NO(\mathbf{r}_{neur}^i,t) = NO_0}$ does not follow any more as the fixed point solution. Rather, one needs to consider the fact that, given the recurrent network topology, the steady state of $\mathrm{NO(\mathbf{r}_{neur}^i)^* = NO(\mathbf{r}_{neur}^i,V_t^1,...,V_t^n)^*}$ in turn depends on the set of thresholds. Unfortunately, this increase in complexity would presumably make it impossible to find a general analytic description of the fixed point similar to the one introduced and discussed in Section \ref{Matrix_Diff_Model_Section}. Moreover, while this modification would provide a way to incorporate network topology into the theoretical steady state of the system for finite diffusion constants, it is not clear whether it would allow perturbations (e.g. due to external input) to be actually sustained longer.

@@

\section{Conclusion and Outlook}\label{Conclusion_Section}
Drawing a conclusion from our results presents itself as a somewhat ambiguous task. On a phenomenological level, our main goal of allowing the LIF-SORN to exhibit a broad, skewed distribution was achieved. However, whether the implications of the diffusive model that revealed itself upon deeper investigations are acceptable in terms of biological plausibility is still left open to debate.

@@

With regard to the future use and implementation of diffusive homeostasis, it could be desirable to cover the essential effects in a more simple and abstract formalism. As shown in Section \ref{Mean_Field_Review_Section}, a simple mean field model as presented by Sweeney et al. still carries problems similar to those of single-neuron homeostasis. However, modifications of this model that incorporates our remarks in Section \ref{Possible_Modifications_Section} might be able to recover properties of the full diffusive homeostatic feedback while being more computationally efficient.

>>>>

As an additional possibility of spike-train analysis, we looked at potential correlations across neurons within both populations. To do so, we calculated cross-correlations for all possible neuron-pairings within a population, excluding auto-correlations. Figure \ref{Pop_Mean_Cross_Corr} shows the mean cross-correlation taken over all these pairs. Surprisingly, we found a significant increase in correlation across neurons for diffusive homeostasis. 
\begin{figure}

\includegraphics[width=\textwidth]{../../plots/Spike_Stats/pop_mean_cross_corr.png}
\caption{Mean of cross correlation over all pairs of neurons in the respective neuron-group. Significantly higher correlation can be found in both groups for diffusive homeostasis. Spike data was taken from $\mathrm{1400-1500\,s}$ of the simulation.}
\label{Pop_Mean_Cross_Corr}
\end{figure}
When speculating about the root of this discrepancy one could consider two possibilities: Either, it is an immediate consequence of diffusive homeostasis, or it is indirectly related through other mechanisms present within the network. Regarding the first, it is certainly true that some amount of information about the activity of one neuron is transferred to another one in its neighborhood via diffusion. However, due to the time scale of the homeostatic adaption, the response to fluctuations in the diffusive signal is on the order of seconds, while correlations in Figure \ref{Pop_Mean_Cross_Corr} are taking place within milliseconds. Thus, we concluded that a \emph{direct} link between homeostatic signaling and increased correlations can be regarded as implausible and that it must be an effect based on topological differences within the network. We investigate these in Section \ref{Network_Topology_Section}.

@@

Despite of fluctuations within the firing rate on small time scales due to the inherent nature of - approximately - random spike generation, we wanted to know how strongly firing rates of single excitatory cells fluctuate over longer timescales of multiple seconds. This question is not only of relevance with respect to the "stiffness" of homeostasis, but also relates to the plot in Figure \ref{Fir_Rate_Dist_Compare}: If firing rates fluctuate too much during the period over which means were calculated, the resulting distribution might be narrower than what one could expect from a distribution of "momentary" rates. A constant "rate" of an approximately randomly spiking neuron means that the dependence of fluctuations of rates onto the width of the averaging window should be identical to a homogeneous poisson process of the same total mean firing rate. As bin sizes increase, possible long-term fluctuations of firing rates can then be identified as deviations from the variance one would expect from a homogeneous process. We tested this in Figure \ref{f_Var_vs_n_Bin}. (A) was taken from $\mathrm{1000-1500\,s}$, which is well inside the phase of diffusive homeostasis. As one can see, the statistics of the three representative neurons are well fitted by the predictions for homogeneous poisson processes with the same mean rate, being a straight line given by $\mathrm{var = f_{mean}\cdot n_{bins}/T_{total}}$, though slight deviations can be seen as a different factor of proportionality. (B) acts as an illustration showing a counterexample: Here, we included the entire time span of the simulation, including the transition between non-diffusive and diffusive homeostasis. For almost all of the neurons, this will cause a transition of firing rate between 3 Hz and a new rate different from 3 Hz. This inhomogeneity is represented by the increasing positive relative deviation from the dashed line for small number of bins (i.e., large bin widths), even increasing again for a very few number of bins.
\begin{figure}
%%% plot_spt_var_vs_bin_width.py
\includegraphics[width=\textwidth]{../../plots/Spike_Stats/sim_f_var_vs_hom_poisson.png}
\caption{A: Relation between Variance of the frequency signal (acquired by binning spikes) and the number of bins within the given time range of $\mathrm{1000-1500\,s}$, taken from three randomly picked excitatory neurons. B: Same procedure as in (A) for a randomly chosen excitatory neuron, but time range was $\mathrm{0-1500\,s}$, which includes the initial phase of non-diffusive homeostasis. In both plots, dashed lines are the expected curve of a homogeneous poisson process of the same mean rate.}
\label{f_Var_vs_n_Bin}
\end{figure}
We therefore concluded that diffusive homeostasis manages to retain firing rates on a constant level, not only population-wise but on a single-cell level as well. In particular, plastic modifications across the network due to STDP and synaptic growth/pruning - which were always acting for all the simulation results presented so far - appeared to be compensated for.

@@

In contrast to our model, Effenberger et al. identified the presence of inhibitory STDP as a necessary mechanism for the development of this feature. On a deeper explanatory level, the authors argue that inhibitory STDP is indirectly involved: It weakens inhibitory currents for some neurons, which cause these neurons to have more above-average firing rates. In turn, synapses between highly active presynaptic cells and postsynaptic neurons with lower activity are known to be subject to long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}. With these causal relations in mind, we can argue that diffusive homeostasis effectively embodies the same functional role as inhibitory STDP in \cite{Effenberger_2015} by allowing for the presence of excitatory cells with above-average activity. We tested this relationship by plotting the mean outgoing weights against the average firing rate, see Figure \ref{Out_Weight_vs_F}. A strong heterogeneity of firing rates allows for the development of few strong synapses, while the distribution of mean weights resulting from a narrow distribution is limited to a smaller range. We also tested the case of instant diffusion. Though firing rates span across a similar range, mean weights do not reach as high values as in the case of diffusion at a finite rate.
\begin{figure}
%%% out_weight_vs_f.py
\includegraphics[width=\textwidth]{../../plots/syn_topology/mean_out_weights_vs_rate.png}
\caption{Mean of outgoing excitatory weights at $\mathrm{t=1500\,s}$ plotted against mean presynaptic firing rate (averaged over $\mathrm{t=700-1000\,s}$) in regular (A) and logarithmic space (B). Each plot corresponds to a presynaptic excitatory cell.}
\label{Out_Weight_vs_F}
\end{figure}
Furthermore, it is interesting to note that on a logarithmic weight scale, we found a roughly linear relationship. Figure \ref{Out_Weight_vs_F} only depicts data from simulations including a distance dependent connection profile, since removing this topology did not result in noticeable differences.
\newpage
\section{Further Analysis of the Firing Rate Distribution}
On a preliminary level, the results of section \ref{Fir_Dist_Section} were positive with respect to our goal of achieving a broad and skewed firing rate distribution. Following this, we tried to further gain insight into the actual shape of the resulting distribution. 
\subsection{Review of a Dynamic Mean-Field Model}\label{Mean_Field_Review_Section}
Sweeney et al. attempted to predict the shape of the firing rate distribution by means of a simplified mean-field approximation of diffusion \cite{Sweeney_Paper}. The main simplification within homeostatic feedback was the replacement of Equation \ref{Theta_dyn} by
\begin{equation}
\dot{V_t^i}(t) = \frac{1}{\tau_{HIP}} \left( (1-\alpha)\frac{\phi_i-\phi_0}{\phi_i} +\alpha \frac{\langle \phi \rangle-\phi_0}{\langle \phi \rangle} \right)\;. 
\label{diff_hom_simpl_sweeney}
\end{equation}
$\mathrm{\alpha \: \epsilon \: [0,1]}$ thereby acted as a parameter that determines the "mixture" between single-neuron-homeostasis ($\mathrm{\alpha=0}$) and the limit of quasi instantaneous spreading of the diffusive signal across the population ($\mathrm{\alpha=1}$). $\mathrm{\phi_i}$ and $\mathrm{\mathrm{\langle \phi \rangle}}$ represent individual firing rates and their overall mean.

@@

\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_sim_vs_mat.png}

@@

\newpage
\subsection{Spreading of NO-sources extends Encoding of Input Heterogeneity}
Since our analytic results revealed that a strong correlation between spatial structure and result firing rates is present if diffusive interaction allows a clear distinction between individual neurons and their spatial neighbors, we considered the possibility that a wider spread of each individual NO-source could locally decrease distinguishability between neurons. Thereby, it might allow input heterogeneities to be encoded over a longer period of time without the need to tweak diffusion to unrealistically high values. The biological plausibility of this idea is discussed in Section \ref{Possible_Modifications_Section}.

@@

Sweeney et al. claimed that their implementation of diffusive homeostasis enables individual neurons to vary their firing rates more flexible compared to single-neuron homeostatic models, especially allowing for sustained encoding of different levels of external input. Interestingly, we could not confirm this, at least within the tests that we performed and the given set of standard parameters. Overall, the resulting behavior of the excitatory population rather appeared to us as a form of single-neuron homeostasis whose individual targets are predetermined by the quenched random spatial structure of the respective cells. In particular, our result depicted in Figure \ref{Ext_Input_Switch} did not support the notion of separability of inputs. Of course, this impression only applies to the case where the aforementioned mixture of influence between spatial and synaptic topology is dominated by the former. By analyzing network activity based on our analytic model, we found that for finite diffusion constants, indeed only a single homeostatic fixed point exists. On a practical level though, the gradual decorrelation with this theoretical state of activity upon larger values of $\mathrm{D}$ is presumably caused by synaptic turnovers, which change the synaptic input. The resulting changes in activity are more slowly and less accurately compensated in the case of larger diffusion constants. However, for the standard choice of parameters (being roughly based on experimental data), the resulting activity is indeed strongly bound to the spatial structure of excitatory cells. Naturally, this raises the question of biological plausibility. To our knowledge, no experimental study exists that relates measurements of spontaneous activity to local fluctuations of neuronal densities. Ivenshitz and Segal studied the influence of (mean) neuronal density onto neuronal activity in a culture of hippocampal neurons \cite{Ivenshitz_2010}. Lower densities resulted in a more irregular activity, with stronger but less frequent bursting events. However, since our network was tuned to exhibit non-bursting activity, it is hard to draw any conclusions from this result.

@@

A major issue of Equation \eqref{Theta_dyn} is the fact that, given a clamped positive or negative difference between the actual NO concentration and the target concentration, the excitability of the neuron would decrease or increase without bounds. Because of the limited amount of ion channels that exist in a cell and can be affected by nitric oxide, upper and lower bounds should certainly be present. A simple approach to tackle this would be to implement hard bounds into our neuron model, not allowing the threshold to pass an upper and lower value. Another possibility is the implementation of these bounds by means of the differential equation itself. In either case, such a modification could break the ability of the network to tune thresholds in such a way that necessarily \emph{all} neurons eventually reach target concentration. As a consequence, the fixed point of firing rates under diffusive homeostasis would not be strictly determined by spatial structure, but by a combination of network structure and the neurons' positions. As an example, consider a modification of Equation \eqref{Theta_dyn} of the form
\begin{equation}
\dot{V_t^i}(t) = \frac{1}{\tau_{V_t}}\left(\frac{NO(\mathbf{r}_{neur}^i,t)-NO_0}{NO_0} + \frac{\alpha}{V_t^i - V_{t,min}} + \frac{\alpha}{V_t^i - V_{t,max}}\right) \; .
\label{Theta_dyn_with_Bounds}
\end{equation}
In this form, $\mathrm{NO(\mathbf{r}_{neur}^i,t) = NO_0}$ does not follow any more as the fixed point solution. Rather, one needs to consider the fact that, given the recurrent network topology, the steady state of $\mathrm{NO(\mathbf{r}_{neur}^i)^* = NO(\mathbf{r}_{neur}^i,V_t^1,...,V_t^n)^*}$ in turn depends on the set of thresholds. Unfortunately, this increase in complexity would presumably make it impossible to find a general analytic description of the fixed point similar to the one introduced and discussed in Section \ref{Matrix_Diff_Model_Section}. Moreover, while this modification would provide a way to incorporate network topology into the theoretical steady state of the system for finite diffusion constants, it is not clear whether it would allow perturbations (e.g. due to external input) to be actually sustained longer.

@@

\newpage
\section{Conclusion and Outlook}\label{Conclusion_Section}
Drawing a conclusion from our results presents itself as a somewhat ambiguous task. On a phenomenological level, our main goal of allowing the LIF-SORN to exhibit a broad, skewed distribution was achieved. However, whether the implications of the diffusive model that revealed itself upon deeper investigations are acceptable in terms of biological plausibility is still left open to debate.

@@

With respect to future use and implementation of diffusive homeostasis, one might desire to cover the essential effects in a more simple and abstract formalism. As shown in Section \ref{Mean_Field_Review_Section}, a simple mean field model as presented by Sweeney et al. still carries problems similar to those of single-neuron homeostasis. However, modifications of this model that incorporates our remarks in Section \ref{Possible_Modifications_Section} might be able to recover properties of the full diffusive homeostatic feedback while being more computationally efficient.
